### 2019-01-02 Sections/economics_of_the_quantum_internet.tex
minor

In this part, it was established how a qubit market can function, and how the pricing mechanisms of various derivatives may work. One of the more interesting dimensions to the development of the quantum internet, is understanding \textit{how} the cooperation\index{Cooperation} between different suppliers will occur. Importantly, the cost of building quantum computers means that there may be a limited number of competing vendors -- for profit maximisation to occur, the most likely outcome is cooperation between them. The main question is, what can be learnt from applying game theoretic techniques to the strategies available to quantum computing vendors? Importantly, what are the implications associated with supply-side shifts, such as the imposition of taxation\index{Taxation}.

@@

The final strategy available to the firms is to consolidate their resources into a distributed cloud computing environment (Sec.~\ref{sec:dist_comp}), where the limitations of a single system are lifted, allowing for even better resource-sharing and improvement beyond what a single system solution can offer. In this scenario, both providers will be able to collaborate such that they can meet their individual computational requirements, without having to fully build independent systems like that in the licensing strategy. Importantly though, while there may be a small loss in utility for one of the parties compared to the licensing strategy, the cooperation allows an overall higher level of utility to be achieved jointly, creating a Nash equilibrium\index{Nash equilibrium} at this point, $C$.

@@

The second question that arises is what happens to the utility payoff matrix when taxation is imposed?\index{Taxation} The assumption that $X$ and $Y$ are operating in similar regulatory environments can be relaxed. As identified in Sec.~\ref{XX}, the imposition of a tax on quantum computing is highly likely given its inelastic nature as a commodity. As such, the question becomes, what happens when $X$ is in a more heavily taxed environment, or something impacts the utility achieved by the players asymmetrically. Economically, a tax operates by transferring utility from the supplier of a good to the government. As shown in the market analysis, this will result in a small reduction in supply, but overall it should remain at a similar level. However, in the cloud computing strategy, even small reductions in supply are exponentially multiplied. The result is that all collaborative strategies will yield less utility for $X$, as it both reduces supply and transfers utility to government. The impact however is also felt by $Y$, as the overall computational power of the cloud is reduced in the cloud computing strategy. This results in a payoff matrix as shown in Tab.~\ref{tab:game_theory_3}.

@@

\begin{itemize}
	\item There is complete cooperation between all suppliers.
	\item Competing cartels develop, where for external reasons (e.g. political, geographical, ideological, strategic), there is a benefit in cooperating with just a few players, and acting as a single supplier in direct competition with other cartels.
\end{itemize}

>>>>

Earlier in this part, it was established how a qubit market can function, and how the pricing mechanisms of various derivatives may work. One of the more interesting dimensions to the development of the quantum internet, is understanding \textit{how} the cooperation\index{Cooperation} between different suppliers will occur. Importantly, the cost of building quantum computers means that there may be a limited number of competing vendors -- for profit maximisation to occur, the most likely outcome is cooperation between them. The main question is, what can be learnt from applying game theoretic techniques to the strategies available to quantum computing vendors? Importantly, what are the implications associated with supply-side shifts, such as the imposition of taxation\index{Taxation}.

@@

The final strategy available to the firms is to consolidate their resources into a distributed cloud computing environment (Sec.~\ref{sec:dist_QC}), where the limitations of a single system are lifted, allowing for even better resource-sharing and improvement beyond what a single system solution can offer. In this scenario, both providers will be able to collaborate such that they can meet their individual computational requirements, without having to fully build independent systems like that in the licensing strategy. Importantly though, while there may be a small loss in utility for one of the parties compared to the licensing strategy, the cooperation allows an overall higher level of utility to be achieved jointly, creating a Nash equilibrium\index{Nash equilibrium} at this point, $C$.

@@

The second question that arises is what happens to the utility payoff matrix when taxation is imposed?\index{Taxation} The assumption that $X$ and $Y$ are operating in similar regulatory environments can be relaxed. As identified in Sec.~\ref{sec:taxation}, the imposition of taxation on quantum computing is highly likely given its inelastic nature as a commodity. As such, the question becomes, what happens when $X$ is in a more heavily taxed environment, or something impacts the utility achieved by the players asymmetrically. Economically, a tax operates by transferring utility from the supplier of a good to the government. As shown in the market analysis, this will result in a small reduction in supply, but overall it should remain at a similar level. However, in the cloud computing strategy, even small reductions in supply are exponentially multiplied. The result is that all collaborative strategies will yield less utility for $X$, as it both reduces supply and transfers utility to government. The impact however is also felt by $Y$, as the overall computational power of the cloud is reduced in the cloud computing strategy. This results in a payoff matrix as shown in Tab.~\ref{tab:game_theory_3}.

@@

\begin{itemize}
	\item There is complete cooperation between all suppliers.
	\item Competing cartels\index{Cartels} develop, where for external reasons (e.g. political, geographical, ideological, strategic), there is a benefit in cooperating with just a few players, and acting as a single supplier in direct competition with other cartels.
\end{itemize}
